The Independence of the Continuum Hypothesis in Isabelle/ZF

### 2022-03-06 src/document/root.tex
Typos, hyphening

\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}
\usepackage[numbers]{natbib}
\usepackage{babel}

@@

\begin{abstract}
  We redeveloped our formalization of forcing in the set theory framework of
  Isabelle/ZF. Under the assumption of the existence of a countable
  transitive model of ZFC, we construct proper generic extensions 
  that satisfy the Continuum Hypothesis and its negation.
\end{abstract}

@@

The main entry point of the present session is the theory
\theory{Defitions\_Main.thy}, in which a path from fundamental set
theoretic concepts formalized in Isabelle reaching our main theorems
is expounded. Cross-references to major milestones are provided there.

>>>>

\documentclass[11pt,a4paper,english]{article}
\usepackage{isabelle,isabellesym}
\usepackage[numbers]{natbib}
\usepackage{babel}

@@

\begin{abstract}
  We redeveloped our formalization of forcing in the set theory framework of
  Isabelle/ZF. Under the assumption of the existence of a countable
  transitive model of $\ZFC$, we construct proper generic extensions 
  that satisfy the Continuum Hypothesis and its negation.
\end{abstract}

@@

The main entry point of the present session is the theory
\theory{Definitions\_Main.thy}, in which a path from fundamental set
theoretic concepts formalized in Isabelle reaching our main theorems
is expounded. Cross-references to major milestones are provided there.
